---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MyStatsPackage)
```

# Introduction
This vignette file was made to describe the functions and data present in the MyStatsPackage project made for MATH 4754

## The first function: myboot2

The first function is the myboot2 function that returns a histogram for a chosen statistic, i.e. mean, chi-squared, given x data set, a function to apply to the data and an alpha value to find the conf interval
```{r}
set.seed(35); 
y = round(rnorm(30, mean=20, sd=3),3)
myboot2(x=y, fun="sd", alpha =0.3)
```

## the second funtion: FetchCSV
The FetchCSV function returns a data table using data frame. The specific path of the data set must be known.
```{r}
df = FetchCSV("C:/Statistics2022/ASS/ASS4/NZBIRDS.csv")
df
```

## Third Function: myfunddt 
The myfunddt function returns a graph for the ddt data frame. Specifically, it plots Length vs Weight and adds a quadratic model
```{r}
ddt = FetchCSV("C:/Statistics2022/Labs/Lab1/DDT-1.csv")
myfunddt(df = ddt, Species = "CCATFISH") 
```

## Fourth Function: myncurve
myncurve is a function that returns a plot of the normal distribution with the area/probability shaded in and written on the graph. Also lists the area into the command-line.

```{r}
myncurve(10, 5, 6)
```

